---
title: "Chapter 2"
subtitle: "R Markdown: The Definitive Guide"
author: "Tom Madsen"
date: "2023-08-17"
format:
    html:  
        self-contained: true
        toc: true
        toc_depth: 2
        dev: svg
        theme: lumen
        # include-in-header: header.html
        # include-before-body: before.html
---

Link to book [https://bookdown.org/yihui/rmarkdown/](https://bookdown.org/yihui/rmarkdown/)

This is a paragraph in an R Markdown document.

Below is a code chunk:

```{r}
fit = lm(dist ~ speed, data = cars)
b = coef(fit)
plot(cars)
abline(fit)
```

```{r}
knitr::kable(iris[1:5, ], caption = 'A caption')
```
The slope of the regression is `r b[2]`.

### 2.5.1 Inline formatting

**Bold** text.

using subscripts example: H~3~PO~4~

using superscripts example: Cu^2+^

Refer to the footnote^[This is a footnote]

> "I thoroughly disapprove of duels. If a man should challenge me, I would take him kindly and forgivingly by the hand and lead him to a quiet place and kill him."
>
> --- Mark Twain




In R, the character
# indicates a comment

The result of 5
- 3 is 2.

### 2.5.3 Math expressions

$$
P(E) = {n \choose k} p^k (2-p)^{n-k}
$$

```{python}
import sys
print(sys.version)
import matplotlib.pyplot as plt
plt.plot([0,2,1,4])
plt.show()
x = 'This is an example in python'
y = 10
```


```{bash}
echo "Hello Bash!"
ls
```

### 2.7.5 Stan



## 2.8 Interactive documents

Below is a map that shows the location of the Department of Statistics, Iowa State University.

```{r out.width='100%', echo=FALSE}
library(leaflet)
leaflet() |>
  addTiles() |>
  setView(-93.65, 42.0285, zoom = 17) |>
  addPopups(
    -93.65, 42.0285,
    'Here is the <b>Department of Statistics</b>, ISU'
  )
```

Below is a map that shows location of the SIAD

```{r out.width='100%', echo=FALSE}
library(leaflet)
leaflet() |>
  addTiles() |>
  setView(-112.5418, 40.8884, zoom = 17) |>
  addPopups(
    -112.5418, 40.8884,
    'Here is the <b>SIAD</b>, Toole County'
  )
```
